\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{0pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\begin{document}
\begin{center}
    \textbf{\Huge \scshape Sahilkumar Prasad} \\ \vspace{1pt}
    \textbf{\Large Java Backend Developer} \\ \vspace{2pt}
    \small +91-8451968851 $|$ \href{mailto:prasadsahil06@gmail.com}{\underline{prasadsahil06@gmail.com}} $|$
    \href{https://www.linkedin.com/in/sahilkumar-prasad-74abba272/}{\underline{LinkedIn}} $|$
    \href{https://github.com/sahill1001}{\underline{Github}}
\end{center}

%-----------Summary-----------
\section{Summary}
Java Backend Developer (2.5 years) building reliable, low-latency services with Java, Spring Boot, and Microservices on Azure. Strong in Data Structures \& Algorithms and System Design (HLD/LLD). Product mindset, clean architecture, performance, and resilience focused.

%-----------Skills-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Languages}: Java, JavaScript, SQL
    \item \textbf{Java Frameworks}: Spring Boot, Spring MVC, Spring Security, JPA/Hibernate, Maven
    \item \textbf{Databases}: MySQL, PostgreSQL, Oracle, Redis
    \item \textbf{Cloud/DevOps}: Azure, Docker, Jenkins, Git, Linux, CI/CD
    \item \textbf{Backend Technologies}: REST APIs, Microservices, Distributed Systems, Caching, Messaging (Kafka), HLD/LLD, Data Structures \& Algorithms
 \end{itemize}

%-----------Experience-----------
\section{Professional Experience}
  \begin{itemize}[leftmargin=0.15in]
    \resumeSubheading
      {Crescent Engineering and Consulting}{Vashi, New Mumbai}
      {Java Backend Developer}{May 2023 -- Present}
      \begin{itemize}
        \resumeItem{Shipped 5+ backend services (Spring Boot, Java); improved system performance by ~40\% and lowered P95 latency.}
        \resumeItem{Designed and implemented RESTful APIs and Microservices; reduced average response time by ~45\% via caching/IO tuning.}
        \resumeItem{Modeled relational schemas and optimized SQL (indexes, query plans); cut DB P95 by ~50\%.}
        \resumeItem{Owned Azure deployments with Docker and Jenkins pipelines; improved reliability and deployment lead time.}
        \resumeItem{Raised code quality with reviews, tests, and observability; reduced production defects by ~40\%.}
      \end{itemize}
  \end{itemize}

%-----------Projects-----------
\section{Key Projects}
  \begin{itemize}[leftmargin=0.15in]
      \resumeProjectHeading
        {Enterprise Management System}{Spring Boot, MySQL, Azure}
        \begin{itemize}
          \resumeItem{Built inventory/finance modules with REST APIs and layered architecture (Controller-Service-Repo).}
          \resumeItem{Leveraged JPA/Hibernate; introduced caching (Redis) to reduce hot-path latency under load.}
          \resumeItem{Enabled horizontal scaling with stateless services and DB connection pooling.}
        \end{itemize}
      \resumeProjectHeading
        {E-Commerce Backend API}{Spring Boot, PostgreSQL, Redis, Docker}
        \begin{itemize}
          \resumeItem{Designed microservices (catalog, users, orders) with clear domain boundaries and contracts.}
          \resumeItem{Added Redis caching and API rate limiting; improved throughput and stability during peak traffic.}
          \resumeItem{Containerized and shipped with Docker; reduced deployment time and environment drift.}
        \end{itemize}
      \resumeProjectHeading
        {Banking System Backend}{Java, Spring Security, Oracle, JWT}
        \begin{itemize}
          \resumeItem{Implemented JWT-based auth\,/\,authorization; added transaction APIs with idempotency and validation.}
          \resumeItem{Modeled accounts\,/\,transactions ensuring ACID guarantees and consistent balances.}
          \resumeItem{Improved auditability with structured logging\,/\,trace IDs and centralized error handling.}
        \end{itemize}
  \end{itemize}

%-----------Education-----------
\section{Education}
  \begin{itemize}[leftmargin=0.15in]
    \resumeSubheading
      {University of Mumbai}{Mumbai, India}
      {B.Sc Computer Science | CGPA: 9.57}{2020 -- 2023}
  \end{itemize}

%-----------Achievements-----------
\section{Achievements}
\begin{itemize}
    \item Optimized database queries and added caching, reducing API response time by ~50\% in production.
    \item Implemented microservices architecture that improved horizontal scalability and fault isolation.
    \item Built reusable Spring Boot components and templates, reducing feature delivery time by ~35\%.
\end{itemize}

\end{document}


